Real-space computation of $E$/$B$-mode maps I: Formalism and Compact Kernels

### 2017-11-02 articles/formalism/sections/introduction.tex
brainstorming in the intro

\section{Introduction}
In this work we follow the convection in which bar-ed variables correspond to those in real space, while the tilde-ed variables correspond to those in harmonic space \cite{Zaldarriaga2001a}.

>>>>

\section{Introduction}
The Cosmic Mircowave Background is 10 percent polarized, but the polarization contains independent cosmological information.

Standard technique is to convert Stokes parameters into scalar and pseudo-scalar modes, which are easier to compare to theory.

The pseudo-scalar $B$ mode is particularly important because it cannot be generated by primordial scalar pertubations

primordial tensor perturbations

lensing of $E$-modes

systematics checks

exotic phenemena like cosmic birefringence

The spin-0 $E$/$B$ modes relate to the spin-2 Stokes parameters via the spin-raising and -lowering operators ($\eth,\bar \eth$), which are second derivatives evaulated locally.  However, in practice we compute $E$/$B$ modes to a specified band limit, and this makes them non-local functions of the polarization field.  In other words, the $E$/$B$ modes at a point can get contributions from all over the sky.

(stuff about foregrounds, masking, ambiguous modes with references)

Zaldarriaga explored the spatial real-space kernels in the flat-sky approximation \citep{}.

In this work we follow the convection in which bar-ed variables correspond to those in real space, while the tilde-ed variables correspond to those in harmonic space \cite{Zaldarriaga2001a}.
